SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-04-28 docs/computEL-final/paper.tex
Edit email addresses.

\author{Guy Emerson, Liling Tan, Susanne Fertmann, Alexis Palmer and Michaela Regneri \\
Universität des Saarlandes \\
Campus, 66123 Saarbrücken, Germany \\
{\tt liling.tan@uni-saarland.de, emerson@coli.uni-saarland.de,} \\
{\tt susfert@coli.uni-saarland.de, apalmer@coli.uni-sb.de,}\\
{\tt regneri@coli.uni-saarland.de}}

\date{}

>>>>

\author{Guy Emerson, Liling Tan, Susanne Fertmann, Alexis Palmer and Michaela Regneri \\
Universität des Saarlandes \\
66123 Saarbrücken, Germany \\
{\tt \{emerson, liling, susfert, apalmer, regneri\}@coli.uni-saarland.de} \\
%{\tt susfert@coli.uni-saarland.de, apalmer@coli.uni-sb.de,}\\
%{\tt regneri@coli.uni-saarland.de}}
}
\date{}
